### 2017-03-30 paper/frag_implementation.tex
Some progress on paper

In order to create the tunnels, the detour runs two IPTables commands, which
create NAT rules.

>>>>

In order to create the tunnels, the detour runs two IPTables commands, which
create NAT rules. The first performs DNAT:

\begin{lstlisting}
iptables -t nat -A PREROUTING \
         -s (*\emph{ClientAddress}*) \
         -d (*\emph{DetourAddress}*) \
         -p tcp --dport (*\emph{DetourPort}*) \
         -j DNAT --to (*\emph{RemoteAddress}*):(*\emph{RemotePort}*)
\end{lstlisting}

In this command, we add to the \texttt{nat} table, on the \texttt{PREROUTING}
chain. Incoming packets from the client, addressed to the agreed upon
\textit{DetourPort} are sent to the \texttt{DNAT} chain, which rewrites the
destination address to be the agreed upon remote address and port. This must
occur before the kernel routes the packet. Once the kernel has routed the
packet, the DNAT rule can be applied:

\begin{lstlisting}
iptables -t nat -A POSTROUTING \
         -s (*\emph{ClientAddress}*) \
         -d (*\emph{RemoteAddress}*) \
         -p tcp --dport (*\emph{RemotePort}*) \
         -j SNAT --to (*\emph{DetourAddress})
\end{lstlisting}

Since the destination address and port have already been modified, this rule
looks for packets addressed to the remote address and port, but still using the
client address as the source. It jumps these packets to the DNAT chain, where
their source address will be rewritten as the detour's address.

It is important to understand that these rules are generally only applied to the
initial SYN segment of the TCP flows. Once these rules are applied, the
connection tracking mechanism of the kernel takes over, ensuring that these
rules are applied in reverse to response packets.

The detour daemon is implemented as a Python script. It listens for tunnel
requests, executes the correct commands to create them, and then sends
responses. It ensures that detour ports do not collide with each other, or with
ports that are open on the daemon machine. It also ensures that on termination,
all tunnels are torn down.

This mechanism has the advantage that it requires zero overhead. Since no
headers are added, the full amount of data may be transmitted on these segments.
However, its disadvantage is that tunnels must be configured each time a new
connection is created on the client. While the client may simply send packets to
a new remote through an OpenVPN tunnel, it must incur a RTT delay requesting a
new tunnel from the NAT detour before it can begin establishing a subflow.

\subsection{Client Daemon}

In order for the client to use detours, it must either initiate OpenVPN
connections with them, or dynamically request tunnels via the UDP protocol. In
either case, a client program must manage these activities. In particular, a
program must be able to notify the kernel when new detours are available for
immediate use, and it must be able to respond to requests from the kernel for
new detours. The mechanism for communication with the kernel will be discussed
in the following section.

\subsubsection{OpenVPN Client Management}

The client daemon reads a configuration file which informs it of detours which
use OpenVPN. On startup, it initiates an OpenVPN connection with each detour.
Once the connections are established, it sends a message to the kernel with the
virtual network device's name.

\subsubsection{NAT Client Management}

In order to use NAT tunnels, the client daemon must be much more complex. The
client waits for kernel tunnel requests. Upon receiving these requests, it sends
a UDP request to each NAT detour server specified in its configuration file. It
then waits for responses from the detour servers. Upon receiving each response,
it sends a reply back to the kernel notifying it of the new NAT tunnel.

\subsection{Client Communication}

In order to communicate between kernel and userspace, we use Generic Netlink
sockets. Netlink is an address family for the socket interface
(\texttt{AF\_NETLINK}, similar to \texttt{AF\_INET}), which allows just this
sort of communication. There are several types of Netlink socket, but the
Generic Netlink type allows any kernel component to define its own protocol,
while still managing marshalling data.

Our protocol is similar to the UDP protocol for communication between the client
and detour. The kernel sends a message of type \texttt{DETOUR_C_REQ} to a
``multicast group'' which the client daemon subscribes to. This message contains
the necessary parameters (remote address, remote port). The client daemon may
reply to the kernel with \texttt{DETOUR_C_ADD} commands, which add detour
entries, and \texttt{DETOUR_C_DEL} commands, which remove them.

The protocol allows the client to register both OpenVPN and NAT based detours,
both of which are supported in the kernel implementation.

\subsection{Client Kernel}

Finally, the client kernel must be capable of requesting detours, receiving
information from userspace, and using that information to establish subflows.
Support for this functionality is implemented as a Linux kernel module. In
particular, it is implemented as a MPTCP ``path manager.'' A path manager is a
kernel module which makes decisions regarding when to advertise additional
addresses and when to create new subflows. An instance of the path manager is
created for each MPTCP connection, when the connection becomes fully established
(that is, after the third packet in the handshake).

Upon creation, our path manager enqueues a task to be executed in a long-running
kernel thread. This task first sends a message to userspace on the Generic
Netlink socket, requesting a detour. Then, the task looks through an internal
list of detours. The kernel maintains two lists of detours. The first is a list
of OpenVPN detours. These detours are not specific to the remote port and host.
The second list contains NAT tunnels which were created by the client daemon and
sent to the kernel via the \texttt{DETOUR_C_ADD} command.

The task attempts to add up to $N$ subflows, where $N$ is a configurable limit.
If it cannot (due to lack of subflows), it terminates. If OpenVPN detours are
available, then they take precedence over the NAT detours, because they are
available immediately.

When the client receives a \texttt{DETOUR_C_ADD} command, it first adds the
details of the tunnel to its internal list. Then, if the tunnel was a NAT
tunnel, it wakes all the path managers so that they can attempt to create a
subflow through that tunnel.
